### 2019-05-07 doc/bilevel/main.tex
notes in Abstract on what we need to do next

%------- Abstract (max 3 pages)
\paperabstract{
We describe capabilities for modeling bilevel and multilevel programs
within the Pyomo modeling software.  These capabilities include
modeling components that represent subproblems, modeling transformations
for re-expressing models with bilevel structure in other forms, and
optimize bilevel programs with meta-solvers that apply transformations
and then perform optimization on the resulting model.  We illustrate
the application of Pyomo to model powergrid reliability problems.
}
%This is an example of the short abstract template (max 3 pages) and how to cite (max 3) references \ref{CY59}, \ref{CP61}.

>>>>

%------- Abstract (max 3 pages)
\paperabstract{
We will use this file to document the following:\\
1. Bilevel model forms\\
\indent	a. Canonical Model Form (e.g., generic affine or convex constraints, discrete variables?)\\
\indent	b. Numerical Example\\
\indent	c. Current Pyomo Code for (a)\\
\indent	d. How would this be solved?\\
2. Uncertainty model forms\\

}
%This is an example of the short abstract template (max 3 pages) and how to cite (max 3) references \ref{CY59}, \ref{CP61}.
